\documentclass[a4paper, 12pt]{article}
%\topmargin-1.5cm

\usepackage{fancyhdr}
\usepackage{pagecounting}
\usepackage[dvips]{color}

% Color Information from - http://www-h.eng.cam.ac.uk/help/tpl/textprocessing/latex_advanced/node13.html

% NEW COMMAND
% marginsize{left}{right}{top}{bottom}:
%\marginsize{3cm}{2cm}{1cm}{1cm}
%\marginsize{0.85in}{0.85in}{0.625in}{0.625in}

%\advance\oddsidemargin-0.85in
%\advance\evensidemargin-0.85in
%\textheight8.5in
%\textwidth6.75in
\newcommand\bb[1]{\mbox{\em #1}}
\def\baselinestretch{1.25}
%\pagestyle{empty}
\newcommand{\hsp}{\hspace*{\parindent}}
\definecolor{gray}{rgb}{0.4,0.4,0.4}

\newcommand{\authorname}{Kathryn~D.~Huff }
\newcommand{\authoremail}{katyhuff@gmail.com}
\newcommand{\authorsite}{katyhuff.github.com}

\begin{document}
\pagestyle{fancy}
%\pagenumbering{gobble}
%\fancyhead[location]{text} 
% Leave Left and Right Header empty.
%\lhead{}
%\rhead{}
%\rhead{\thepage}
\lhead{\textcolor{gray}{\it \authorname}}
\rhead{\textcolor{gray}{\thepage/\totalpages{}}}
\renewcommand{\headrulewidth}{0pt} 
\renewcommand{\footrulewidth}{0pt} 
\fancyfoot[C]{\footnotesize \textcolor{gray}{\authorsite}} 

\begin{center}
{\LARGE \bf Importance of BIDS Resources}\\
\vspace*{0.1cm}
{\normalsize \authorname (\authoremail)}
\end{center}
%\vspace*{0.2cm}

%\begin{document}
%\centerline {\Large \bf Research Statement for \authorname}
%\vspace{0.5cm}

% Write about research interests...
%\footnotemark
%\footnotetext{Check This}

% Your response to the “call for participation” should be a 2-3 page document 
% that describes your efforts in data science, including your challenges and 
% opportunities. We are not asking for a budget or a formal proposal. Instead, 
% please provide an overview of the scientific goals and vision and how working 
% within a lager data science context will further that vision. Our intent is 
% two-fold:  To build a community of data science, and help us steer and evolve 
% the mission of BIDS; and to help attract funding from other sources, including 
% new grants, support from private donors, and corporate sponsorships.

\section*{\textcolor{gray}{\it Cross-Pollination of Ideas}}
% Introduction
I hope to establish a research program capable of tackling a 
variety of challenges in nuclear energy from the technical to the political.  
I expect that BIDS will play a key role by introducing me to a 
community with whom I can share efficient and powerful 
data analysis methods, by exposing me to new research directions, and 
supporting my efforts to adopt new best practices into my work.

The tenets of scientific endeavor (e.g., data control, reproducibility, 
comprehensive documentation, and peer review) suffer in projects that fail to 
make use of current development tools such as unit testing, version control, 
automated documentation and others \cite{wilson_best_2014, 
merali_computational_2010}.  Maintenance of rigorous scientific computing 
standards will help my research program avoid such pitfalls 
\cite{huff_rapid_2011} and incorporation of new methods for efficient and 
accurate use of the data I rely on in reactor physics will keep my research 
program relevant.

\section*{\textcolor{gray}{\it Contributing to the Conversation}}

Additionally, I would be thrilled for the opportunity to participate in the 
working group efforts and conversations. I am deeply passionate about many of 
the working group topics. Most specifically, my volunteer time as a Software 
Carpentry team member, SciPy (Scientific Computing with Python) Conference 
organizer, and scientific community member has emphasized reproducibility, open 
science, and scientific computing education. Also, my combined academic 
aspirations, skill set, and educational background have provided me with a very 
personal perspective on the importance of a novel approach to academic career 
paths in scientific computing.

I believe the BIDS working groups have the unique potential to frame the 
worldwide conversation around these topics and to cultivate solutions by drawing 
on a shrewd, inventive community that is passionate about the future of science.  
I very much hope to continue to be included in the high level of conversation in 
which this community will be engaged.

\bibliographystyle{unsrt}
\bibliography{resources}

\end{document}

